Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-10-08 path_theorems.tex
Cutting out unneeded parts of the paper.

We can examine the difference in radius $r$ and angle $theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof. Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section. We can use \ref{eq:r-deriv-2} to obtain the following:

@@

\begin{corollary}
  The fastest path $\bhat{\gamma_p}$, given the conditions set forth in theorem \ref{theorem:restricted-theta}, will trace out a path which contains an arc of a circle with radius $\bar{v}^2 / \bar{a}^2$ connected to a straight line tangent to the arc.
\end{corollary}

\begin{corollary}
  Given conditions set forth in theorem \ref{theorem:restricted-theta}, we have:
  \begin{eqnarray}
    T_f(\bhat{\gamma_p}) = v_0 \left( \left( \pi - \arccos \frac{R_{min}}{d - R_{min}} \right) 2 \pi R_{min}  + \sqrt{d^2 - 2 R_{min} d}  \right)
  \end{eqnarray}
\end{corollary}

>>>>

We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof. Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section. We can use \ref{eq:r-deriv-2} to obtain the following:

@@
